---
title: "R Notebook"
output: html_notebook
---

Heart Disease Data set
Link: https://archive.ics.uci.edu/ml/datasets/Heart+Disease

using web extension to view name file : https://filext.com/file-extension/NAMES

This directory contains 4 databases concerning heart disease diagnosis.
All attributes are numeric-valued.The data was collected from the four following locations
   
    1. Cleveland Clinic Foundation (cleveland.data)
    2. Hungarian Institute of Cardiology, Budapest (hungarian.data)
    3. V.A. Medical Center, Long Beach, CA (long-beach-va.data)
    4. University Hospital, Zurich, Switzerland (switzerland.data)
    
Each database has the same instance format.  While the databases have 76
raw attributes, only 14 of them are actually used.  Thus I've taken the
liberty of making 2 copies of each database: one with all the attributes
and 1 with the 14 attributes actually used in past experiments.

The authors of the databases have requested:

      ...that any publications resulting from the use of the data include the 
      names of the principal investigator responsible for the data collection
      at each institution.  They would be:

       1. Hungarian Institute of Cardiology. Budapest: Andras Janosi, M.D.
       2. University Hospital, Zurich, Switzerland: William Steinbrunn, M.D.
       3. University Hospital, Basel, Switzerland: Matthias Pfisterer, M.D.
       4. V.A. Medical Center, Long Beach and Cleveland Clinic Foundation: Robert Detrano, M.D., Ph.D.
       
Relevant Information:
     
     This database contains 76 attributes, but all published experiments
     refer to using a subset of 14 of them.  In particular, the Cleveland
     database is the only one that has been used by ML researchers to 
     this date.  The "goal" field refers to the presence of heart disease
     in the patient.  It is integer valued from 0 (no presence) to 4.
     Experiments with the Cleveland database have concentrated on simply
     attempting to distinguish presence (values 1,2,3,4) from absence (value
     0).  
   
     The names and social security numbers of the patients were recently 
     removed from the database, replaced with dummy values.

     One file has been "processed", that one containing the Cleveland 
     database.  All four unprocessed files also exist in this directory. 

5. Number of Instances: 
        Database:    # of instances:
          Cleveland: 303
          Hungarian: 294
        Switzerland: 123
      Long Beach VA: 
      
7. Attribute Information:
   -- Only 14 used
      -- 1. #3  (age)       
      -- 2. #4  (sex)       
      -- 3. #9  (cp)        
      -- 4. #10 (trestbps)  
      -- 5. #12 (chol)      
      -- 6. #16 (fbs)       
      -- 7. #19 (restecg)   
      -- 8. #32 (thalach)   
      -- 9. #38 (exang)     
      -- 10. #40 (oldpeak)   
      -- 11. #41 (slope)     
      -- 12. #44 (ca)        
      -- 13. #51 (thal)      
      -- 14. #58 (num) 
    

Class distribution      
     Database:   0   1   2   3   4 Total
    Cleveland: 164  55  36  35  13   303
    Hungarian: 188  37  26  28  15   294
  Switzerland:   8  48  32  30   5   123
Long Beach VA:  51  56  41  42  10   200
```{r}

# load the library
x <- readLines(url('http://archive.ics.uci.edu/ml/machine-learning-databases/heart-disease/hungarian.data'))

df <- read.table(text = paste(sapply(split(x, 
                                           rep(seq(length(x) / 10), each = 10)), 
                                     paste, collapse = ' '), collapse = '\n'))
df

```


```{r}
realestate

```


